%-------------------------
% Resume in Latex
% Author : Andrew Fandrianto
% License : MIT
%------------------------

\documentclass[letterpaper,9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \underline{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeMonoSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeDoubleSubheading}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://g.co/kgs/DsNwjE}{\Large Andrew Fandrianto}} & \href{mailto:andrew@fto.xyz}{andrew@fto.xyz}\\
  {Full Stack ML Engineer \& ``Engineer's'' People Manager} & {\href{https://github.com/laundry}{github.com/laundry}, \href{tel:+14124555404}{+1-412-455-5404}} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeDoubleSubheading
      {Apple}{Cupertino, CA}
      {Machine Learning Engineering Manager, AIML}{2021-present}
      {Machine Learning Engineer, AIML}{2019-2021}
      \resumeItemListStart
        \resumeItem{Applied machine learning with external impact}
          {
              \newline \textbf{Impact}: Improved quality of 7+ domains through 30+ statistically significant launches, about half requiring ML.
              Led and contributed to search quality projects for Siri, Safari, and Spotlight.
              \newline \textbf{Scope}: Directly handled a majority of the end-to-end process: \{ideation, privacy review, team management, xfunc collaboration/pitching, goal setting, device ground truth testing, backend migrations, data pipelines, server models, on-device models, eval, debug, launch, landing, metrics, monitoring, automation, postmortems\}.
          }
          \resumeItemListStart
            \resumeItem{User Feedback}
            {
                Team and I built a comprehensive, debuggable framework to leverage user feedback. This framework is used by 10+ projects including our team directly and xfunc collaborators.
            }
            \vspace{4pt}
            \resumeItem{Web Answers}{E.g. [why is the ocean blue]. Improved Web Answers coverage by +xx\% relative with models, classic and dense retrieval, query sampling, and practical hacks.}
          \resumeItemListEnd
          \vspace{4pt}
        \resumeItem{Built a team and helped grow the organization}
          {
              Concurrently managing 7 (max 10) individual contributors. Directly hired 10+. Built and ramped a new team from scratch.}
      \resumeItemListEnd
      
    \resumeDoubleSubheading
      {Google}{Mountain View, CA}
      {Software Engineer, Search Quality}{2018-2019}
      {Software Engineer, Research}{2014-2018}
      \resumeItemListStart
        \resumeItem{Applied machine learning with external impact}
          {
              \newline \textbf{Impact}: Led and/or contributed to projects for Search, Google Play, and the TensorFlow ecosystem \{ops, TensorBoard\}.
              \newline \textbf{Scope}: Typically handled these pieces: \{data, model, eval, debug, launch, landing\}.
          }
          \resumeItemListStart
            \resumeItem{Related Answers}{E.g. [why does reading on a train make me sleepy]. Text modeling for snippet ranking with BERT++. Led subgroup, mentored incoming engineers, improved xx\% of Google Search and Assistant traffic.}
            \resumeItem{Short Answers}{E.g. [what is the most abundant gas in venus]. Started cross functional effort between research and product engineering, jointly led subgroup, improved x\% of Google Search and Assistant traffic.}
            \resumeItem{Play Store Search}{Image modeling for app search quality with ImageNet++. Generated +\$xxM revenue.}
          \resumeItemListEnd
          \vspace{4pt}
        \resumeItem{Kaggle, but in Google}
          {
              \newline 2nd engineer for frontend/backend for our internal Kaggle website on Flex AppEngine, used by 20+ teams.
              \newline Owned datasets for internal/external machine learning research (n*100GB-m*1PB)
              \href{https://github.com/google-research-datasets/wiki-reading}{github.com/google-research-datasets/wiki-reading}
          }
      \resumeItemListEnd

    \resumeSubheading
      {eBay}{San Jose, CA}
      {Software Engineer}{2013-2014}
      
    \resumeSubheading
      {Language Technologies Institute at CMU}{Pittsburgh, PA}
      {Graduate Research Assistant}{2011-2013}
      
    \resumeDoubleSubheading
      {Microsoft}{Mountain View, CA}
      {Software Development Engineer Intern}{Summer 2011}
      {Software Development Engineer Intern}{Summer 2010}
      
    \resumeSubheading
      {ITA Software (acquired by Google)}{Boston, MA}
      {User Interface Engineering Intern}{Summer 2009}
      
    \resumeSubheading
      {UC Berkeley Bioengineering, Professor Dan Fletcher}{Berkeley, CA}
      {Researcher @ Berkeley Bioengineering Summer Research Program}{Summer 2008}
      
    \resumeSubheading
      {Cisco Systems}{San Jose, CA}
      {Software Developer Intern}{Summer 2006}
      
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeDoubleSubheading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {Master of Language Technologies}{2013}
      {Bachelor of Science in Computer Science}{2011}
    \resumeMonoSubheading
      {The Harker School}{San Jose, CA}
  \resumeSubHeadingListEnd

%-----------Skills-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{People}
      {Technical Lead Manager for 2+ years. Mentored 20+.}
    \resumeSubItem{Computer Languages}
      {Python, Shell, *SQL.}
    \resumeSubItem{Dusty Computer Languages}
      {C++, Golang, Java, Scala, Jsonnet, Borgcfg, C, Javascript, C\#, R, Matlab.}
    \resumeSubItem{Homosapien Languages}
      {Conversant in Indonesian.}
    \resumeSubItem{Things}
      {MapReduce++, Jupyter, pandas/sklearn/etc, TensorFlow, Superset, Presto/Trino, Docker, IntelliJ*, AWS, Git, Vim.}
    \resumeSubItem{Dusty Things}
      {PyTorch, JAX, AppEngine, Perforce, Eclipse, Maven, Postgres, Kubernetes, Hadoop, Argo, Jenkins, Airflow.}
  \resumeSubHeadingListEnd




\end{document}
